---
title: "Shiny application and reproducible pitch"
author: "Yong Bao"
date: "December 13, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This was built as part of assignment for the course Developing Data Products as part of the Coursera Data Science Specialization.

The app developed for the first part of the assignment demo is avalilable at: https://b33lie.shinyapps.io/shiny_app_mtcars/

Source code for ui.R and server.R files are available on the GitHub repo: https://github.com/b33lie/shiny_app_mtcars/

## Web Application Usages

- This is a Shiny web application help the house owners to estimate the house price based on the historical information in Sacramento, CA.
- The house information about the city, zip, number of beds, number of baths, total square feet, and type associated with the house need to be provided by the house owner to estimate the house prices in the market. 

## Sacramento Dataset

The data used in the web app was retrived from the Sacramento dataset from R package "carat". Here's a summary of the Sacramento dataset:

```{r Sacramento, echo = TRUE}
library(caret)
data(Sacramento)
mydata <- Sacramento[,c(1:7)]
str(mydata)
```

## Plot 

The coorelation bewteen predicted and actual house prices in the Scaramento dataset.

```{r coorelation}
set.seed(955)
in_train <- createDataPartition(log10(mydata$price), p = .8, list = FALSE)
training <- mydata[ in_train,]
testing <- mydata[-in_train,]
model.forest <- train(price~., training, method = "rf", trControl = trainControl(method = "cv", number = 3))
testing$pred <- predict(model.forest, newdata = testing)
plot(testing$pred,testing$price, main="Coorelation between predicted and actual house prices", 
  	xlab="Predicted ", ylab="Actual ", pch=19)

```

