---
title: "Shiny application and reproducible pitch"
author: "Yong Bao"
date: "December 13, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This was built as part of assignment for the course Developing Data Products as part of the Coursera Data Science Specialization.

The application can be found in the following link

https://ybao.shinyapps.io/House/

The source code is hosted in the following link

https://github.com/yongb/Developing-Data-Products

## Web Application Usages

- This is a Shiny web application help the customers to estimate the house price based on the total square feet associated with the house.
- The total square feet need to be provided by the customers followed by clicking the "Submit" button. 

## Sacramento Dataset

The data used in the web app was retrived from the Sacramento dataset from R package "carat". Here's a summary of the Sacramento dataset:

```{r Sacramento, echo = TRUE}
library(caret)
data(Sacramento)
str(Sacramento)
```


## Plot 

The coorelation bewteen predicted and actual house prices in the Scaramento dataset.

```{r coorelation}

set.seed(25)
in_train <- createDataPartition(log10(Sacramento$price), p = .8, list = FALSE)
training <- Sacramento[ in_train,]
testing <- Sacramento[-in_train,]
fit= lm(price ~ sqft, data = training)
slope <- coef(fit)[2]
sqft = testing$sqft
pred <- sqft*slope + coef(fit)[1]
plot(pred,testing$price, main="Coorelation between predicted and actual house prices", 
  	xlab="Predicted ", ylab="Actual ", pch=19)

```
